Social Computing Article\thanks{This title is temporary}

### 2013-01-20 Article.tex
Dei uns retoques e incrementei a análise dos gráficos

The series of experiments summarized in~\cite{kearns:experim} are among the first to try to take advantage of the collective's problem-solving abilities to solve classical computer problems. The experiments are mostly based on the concept of coordination: subjects have individual incentives that are expected to drive them to cooperate with one another and lead them toward the collective goal ~\cite{nowak:evolutioncooperation}.

@@

The experiments conducted by~\cite{farenzena:collabem} had human beings trying to solve constraint satisfaction problems, namely Boolean Satisfiability (SAT)~\cite{cook:complexitytheoremproving} and the popular \emph{Sudoku} game~\cite{weber:satsudoku}, with individuals connected through the network being able to exchange partial solutions of the problem in question. There were two main patterns of behaviour observed in this study in regard to copying neighbours' solutions:

\begin{itemize}
	\item Humans might not evaluate the solutions proposed by their peers, instead choosing the most readily available one. On the other hand,~\cite{mason:collablearnet} suggest that their subjects did evaluate the available solutions, although an in-depth analysis of that wasn't provided.
	\item There is a higher probability of individuals copying peers' solutions when those are shared by several neighbours. That behaviour is referred to by the authors as \emph{conformism}. A similar behaviour was observed by~\cite{mason:collablearnet}, even though the experiments used a different problem.
\end{itemize}

@@

We have developed and detailed a novel method for artificial social problem solving which draws inspiration from the {\em Memetic Networks} model proposed by~\cite{araujo:memenet}. It was used it to built a multi-agent system that simulates the experiments of~\cite{farenzena:collabem}, using the model of human behaviour proposed by them. For simplicity, we limited our experiments to the {\em Sudoku} problem. Our goal is verifying whether the strategies employed by humans are competitive with other heuristics. After identifying the points in which those are lacking, we will then propose methods to increase the efficiency of human problem-solving networks.

@@

The experiments conducted by~\cite{farenzena:collabem} point out a series of observations about the dynamics of cooperation in problem solving with human beings. For instance, the authors analysis has shown that human subjects are more likely to engage in the behaviour of copying the most readily available solutions on the graphic interface than in that of copying the most complete solutions. In order to analyse and compare this two behaviours, he have modelled each one of them as a message-selecting metric for the {\em Social Stage}.

@@

@@

Farenzena ~\cite{farenzena:collabem} have stated that, in their settings, {\em "cooperation works because agents can copy each other"}. This was our hypothesis, and our experiments indicate that, indeed, in some of the topologies tested, the {\em copy rate} has a decisive role in enhancing the algorithm's performance (see Figure~\ref{fig:copy_guess_free_most} and Figure~\ref{fig:copy_guess_free_prob}). The graphs in Figure~\ref{fig:copy_guess_free_most} and Figure~\ref{fig:copy_guess_free_prob} - in which the vertical axis represents the number of iterations needed for the agents to solve the problem - both show a maximum in ({\em copy rate}: 7, {\em guess rate}: 0) and a minimum in ({\em copy rate}: 87, {\em guess rate}: 100), indicating that the greater the {\em copy} and {\em guess} rates are, the fewer iterations are needed for the agents to solve the problem. We understand this is due to the fact that some agents of low levels are incapable of solving some instances of the {\em Sudoku} problem, don't knowing the {\em Sudoku} solving rules needed to mark its cells. These agents have no hope solving the problem without some guessing mechanism, and take advantage of high {\em copy rates}, which can be used to correct wrong guesses through copying better agent's solutions. Also, as shown in Figure~\ref{fig:copy_guess_free_prob_num_solution_reached}, there is a correlation between the copy and guess rates and the convergence of the algorithm: the greater they are, the greater is the probability that the agent network will be able to solve the problem.

\begin{figure}
\includegraphics[scale=0.60]{copy_guess_free_most}
\caption{Effects of copy rate and guess rate on the algorithm's performance (scale-free topology with 'pick most filled' selection metric)
}
\label{fig:copy_guess_free_most}
\end{figure}

@@

As can be seen in Figure ~\ref{fig:progression}, our experiments have shown that evaluating the proposed solutions indeed bring significantly better results, despite the fact that humans seemingly avoid that strategy~\cite{farenzena:collabem}. In all topologies, choosing the solution with the largest number of filled cells not only allows agents to solve the instance earlier, but also causes the network to converge faster to the correct solution. That is, once one individual has found the correct solution, that solution spreads faster through the network if the other agents are evaluating the solutions that reach them.

The strategy based on the behaviour observed in humans fared roughly the same as choosing a random neighbour to copy, and both underperformed in comparison to evaluating the solutions according to number of filled cells. This confirms that choosing solutions arbitrarily without taking their content into consideration is prejudicial to the process of problem-solving.

Even so, that behaviour was observed in human networks. Farenzena~\cite{farenzena:collabem} has suggested that human beings behave like that because in the real world the environment continuously selects against ineffective solutions, since a bad choice in solving a real world problem might cause and agent to cease communication. Since neither the original experiments nor our simulation included such a mechanism, the advantages of that process have not been observed, but they might already be good enough that it may not justify the effort for the agents to evaluate the solutions.

@@

Knowing that, systems that take advantage of human computation might take advantage of the computer aspect of human computation to encourage selection of better-evaluated solutions. One possibility is ordering the neighbours according to the quality of their solutions, with better-evaluated ones being displayed first, instead using a pre-specified or random order. However, that might introduce a (BLANK) in the system, while also limiting variability and discouraging individuals that might have eventual more effective evaluation techniques. To avoid that, perhaps simply displaying the evaluation of each solution might be enough to encourage that behaviour.

>>>>

The series of experiments summarized in~\cite{kearns:experim} are among the first to try to take advantage of collective problem-solving abilities to solve classical computer problems. The experiments are mostly based on the concept of coordination: subjects have individual incentives that are expected to drive them to cooperate with one another and lead them toward the collective goal ~\cite{nowak:evolutioncooperation}.

@@

The experiments conducted by~\cite{farenzena:collabem} had human beings trying to solve constraint satisfaction problems, namely Boolean Satisfiability (SAT)~\cite{cook:complexitytheoremproving} and the popular \emph{Sudoku} game~\cite{weber:satsudoku}, with individuals connected through the network being able to exchange partial solutions of the problem in question. In that study a specific pattern of behaviour was observed which suggests that humans might not evaluate the solutions proposed by their peers, instead choosing the most readily available one. That behaviour is referred to as an evidence of conformism by the human subjects. On the other hand,~\cite{mason:collablearnet} seem to suggest that their subjects did evaluate the available solutions, although an in-depth analysis of that fact wasn't provided. That might mean that multiple factors might influence the behaviour of human agents. We analyse possible reasons for that in the \emph{Results} section.

@@

We have developed and detailed a novel method for artificial social problem solving which draws inspiration from the {\em Memetic Networks} model proposed by~\cite{araujo:memenet}. It was used to build a multi-agent system that simulates the experiments of~\cite{farenzena:collabem}, using the model of human behaviour proposed by them. For simplicity, we limited our experiments to the {\em Sudoku} problem. Our goal is verifying whether the strategies employed by humans are competitive with other heuristics. After identifying the points in which those are lacking, we will then propose methods to increase the efficiency of human problem-solving networks.

@@

The experiments conducted by~\cite{farenzena:collabem} point out a series of observations about the dynamics of cooperation in problem solving with human beings. For instance, the authors analysis has shown that human subjects are more likely to engage in the behaviour of copying the most readily available solutions on the graphic interface than in that of copying the most complete solutions. In order to analyse and compare these two behaviours, he have modelled each one of them as a message-selecting metric for the {\em Social Stage}.

@@

\subsection{A Novel Method For Simulating Human Problem-Solving Networks}

@@

The authors of~\cite{farenzena:collabem} have stated that, in their settings, {\em "cooperation works because agents can copy each other"}. Basing ourselves in that statement, we adopted the hypothesis that a higher copy rate would improve performance of the network. On the other hand, regarding the process of guessing we took the opposite standing, that it would decrease performance. We based that hypothesis on the notion that, when an agent makes a guess, it has a high chance of filling a cell with the wrong value. Once that happens, that grid will assuredly be unable to lead to the right solution until the agent copies a grid without errors from one of its neighbours. Therefore, we hypothesised that if an agent can't make a logical move using its level of \emph{Sudoku}-solving skills, it's better for it to wait for its more capable neighbours to improve the solution and copy from them, instead of risking making and incorrect move.

Regarding our first hypothesis, our experiments indicate that, indeed, in some of the topologies tested, the {\em copy rate} has a decisive role in enhancing the network's performance. To our surprise, however, they also indicate that guessing shows no signs of being detrimental to the process. On the contrary, in several cases it actually contributes to advancing the solution. The graphs in Figure~\ref{fig:copy_guess_free_most} and Figure~\ref{fig:copy_guess_free_prob} both show a maximum in ({\em copy rate}: 7, {\em guess rate}: 0) and a minimum in ({\em copy rate}: 87, {\em guess rate}: 100), indicating that the greater the {\em copy} and {\em guess} rates are, the fewer iterations are needed for the agents to solve the problem. We understand this is due to the fact that some agents of low levels are incapable of solving some instances of the {\em Sudoku} problem, not knowing the {\em Sudoku} solving rules needed to mark its cells. These agents have no hope solving the problem without some guessing mechanism, and take advantage of high {\em copy rates}, which can be used to correct wrong guesses through copying better agent's solutions.

The results also differ depending on the copying strategy employed in the \emph{social stage}. It can be observed that the copy rate has more influence over how fast the correct solution spreads through the network if the agents are evaluating their neighbour's solutions. The graph in Figure~\ref{fig:copy_guess_free_most} shows that as copying increases, the number of rounds necessary for all agents to have the correct solution decreases sharply until it stabilizes in a roughly optimal level. Meanwhile, the benefits of guessing are much less pronounced. On the other hand, when the agents don't evaluate the neighbours' solutions, as can be seen in Figure~\ref{fig:copy_guess_free_prob}, their contributions don't differ as much. Those results confirm that the worth of copying increases when the proposed solutions are evaluated.

Also, as shown in Figure~\ref{fig:copy_guess_free_prob_num_solution_reached}, there is a correlation between the copy and guess rates and the convergence of the algorithm: the greater they are, the greater is the probability that the agent network will be able to solve the problem.

\begin{figure}
\includegraphics[scale=0.60]{copy_guess_free_most}
\caption{Effects of copy rate and guess rate on the algorithm's performance (scale-free topology with 'pick most filled' selection metric). The vertical axis represents the number of iterations needed for all the agents to find the correct solution.
}
\label{fig:copy_guess_free_most}
\end{figure}

@@

As can be seen in Figure~\ref{fig:progression}, our experiments have shown that evaluating the proposed solutions indeed brings significantly better results, despite the fact that humans seemingly avoid that strategy~\cite{farenzena:collabem}. In all topologies, choosing the solution with the largest number of filled cells not only allows agents to solve the instance earlier, but also causes the network to converge faster to the correct solution. That is, once one individual has found the correct solution, that solution spreads faster through the network if the other agents are evaluating the solutions that reach them instead of copying an arbitrary one.

The strategy based on the behaviour observed in humans fared roughly the same as choosing a random neighbour to copy, and both underperformed in comparison to evaluating the solutions according to number of filled cells. This confirms that choosing solutions arbitrarily without taking their content into consideration is prejudicial to the process of social problem-solving.

Even so, that behaviour has been observed in human networks. In~\cite{farenzena:collabem} the authors suggest that it is justified in the real world because "in a non-virtual environment, the feedback of the environment can cause an agent to stop communicating, e.g. in the case of injury or death", so there would be no need for an agent to evaluate solutions because the environment is already selecting against ineffective ones. Since neither the original experiments nor our simulation included such a mechanism of natural selection, the advantages of that process have not been observed, but they might already be good enough that it would be unnecessary for the agents to have to spend effort evaluating the solutions.

@@

Knowing that, systems that take advantage of human computation might take advantage of the computer aspect of human computation to encourage selection of better-evaluated solutions. One possibility is ordering the neighbours according to the quality of their solutions, with better-evaluated ones being displayed first, instead using a pre-specified or random order. However, that might introduce an overhead in the system, while also limiting variability and discouraging individuals that might have eventual more effective evaluation techniques. To avoid that, perhaps simply displaying the evaluation of each solution might be enough to encourage that behaviour.
